---
output: github_document
---


<!-- badges: start -->
[![R-CMD-check](https://github.com/NicolasJBM/buildR/workflows/R-CMD-check/badge.svg)](https://github.com/NicolasJBM/buildR/actions)
[![CodeFactor](https://www.codefactor.io/repository/github/nicolasjbm/buildr/badge)](https://www.codefactor.io/repository/github/nicolasjbm/buildr)
[![License: GPL3](https://img.shields.io/badge/License-GPL3.0-yellow.svg)](https://opensource.org/licenses/GPL-3.0)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# buildR <img src="man/figures/logo.svg" align="right" width="120" />

Toolbox to prepare data and build constructs.



## Overview

The *buildR* package gathers several functions to create specific constructs (like faultlines), create and manipulate networks, transform data, and compute aggregates.  


## Installation

Before you can install *buildR* itself, you will need to install from CRAN the following packages:  

```{r, eval = FALSE}
install.packages(c(knitr,
  "stats", "parallel", "pbapply", "utils", "purrr", "tidyr",
  "dplyr", "forcats", "tibble", "tidygraph", "igraph", "gtools",
  "stringr", "intergraph", "networkDynamic", "ndtv", "network"
  ), dependencies = TRUE)
```

Then, install *buildR* from its GitHub public repository:  

```{r, eval = FALSE}
devtools::install.github("NicolasJBM/buildR")
```


## Usage

Since the functions included in this packages can be grouped in families or processes, their use is described in dedicated vignettes:  

- Transforming or aggregating variables;
- Studying networks;
- Computing faultlines.


## Toolboxes

*buildR* is necessary to run *[modlR](https://github.com/NicolasJBM/modlR)* which uses its *boostr* function.

